\subsubsection{buildACompositeGrid}
 
\newlength{\ogenIncludeArgIndent}
\begin{flushleft} \textbf{%
int  \\ 
\settowidth{\ogenIncludeArgIndent}{buildACompositeGrid(}%
buildACompositeGrid(CompositeGrid \& cg, \\ 
\hspace{\ogenIncludeArgIndent}MappingInformation \& mapInfo, \\ 
\hspace{\ogenIncludeArgIndent}const IntegerArray \& mapList,\\ 
\hspace{\ogenIncludeArgIndent}const int \& numberOfMultigridLevels  =1,\\ 
\hspace{\ogenIncludeArgIndent}const bool useOldGrid  =false)
}\end{flushleft}
\begin{description}
\item[{\bf Description:}] 
   Build a CompositeGrid with optional multigrid levels from a set of Mappings.
  This routine will build a CompositeGrid from a list of Mapping's. 
  
\item[{\bf cg (input/output):}]  if useAnOldGrid==true then this holds the old grid on input. On output cg
 holds the new grid.
\item[{\bf mapInfo (input):}]  This object holds a list of Mappings from which we choose a subset to build the grid from.
\item[{\bf mapList (input):}]  indicate which Mappings in mapInfo.mappingList should be added to the CompositeGrid.
    Add mapInfo.mappingList[mapList(i)] for each element of mapList.
\item[{\bf useAnOldGrid (input) :}]  this means we are adding new grids to an existing overlapping grid.
\end{description}
\subsubsection{setGridParameters}
 
\begin{flushleft} \textbf{%
int  \\ 
\settowidth{\ogenIncludeArgIndent}{setGridParameters(}%
setGridParameters(CompositeGrid \& cg )
}\end{flushleft}
\begin{description}
\item[{\bf Description:}] 
     Specify the number of grid points on each grid based on the number of multigrid levels.

\end{description}
