%-----------------------------------------------------------------------
%   Overture Software
%-----------------------------------------------------------------------
\documentclass{article}

% \setlength{\textwidth}{9in}      % page width

% \usepackage{verbatim}
% \usepackage{moreverb}
% \usepackage{graphics}    
% \usepackage{epsfig}    
% \usepackage{calc}
% \usepackage{ifthen}
% \usepackage{float}
% \usepackage{fancybox}

\usepackage{html}

\newcommand{\documentation}{../documentation}


\begin{document}

\begin{center}
{\Large Downloading Software} \\
~~ \\
LLNL Overlapping Grid Project \\
\htmladdnormallink{Centre for Applied Scientific Computing}{http://www.llnl.gov/casc} \\
\htmladdnormallink{Lawrence Livermore National Laboratory}{http://www.llnl.gov}  \\
\htmladdnormallink{Overture}{http://www.llnl.gov/CASC/Overture} 
\end{center}

The latest release is Overture.v24 and cg.v24. 

% The latest release is Overture.v21 and OverBlown.v21.


Overture is a {\bf large} software package. 
% Together with A++ is is on the order of a million lines ?? of code. 
We are working on making it easier to install but it is not trivial to install. 
% Overture has mainly been developed on Sun workstations with the 4.2 compiler.
Our main development platform is Linux Intel (64 bit) with gcc and pgf77 or gfortran.
Overture can also built built on a MAC with OS/X.

{\bf Read some of the 
\htmladdnormallink{documentation}
{http://www.llnl.gov/casc/Overture/henshaw/overtureDocumentation/overtureDocumentation.html}
 first}, such as the primer, to get an idea of
what Overture does before spending the time to install the software.

%  Some users have been able to build Overture under Windows with Cygwin.
%  (see \htmladdnormallink{http://slyi.ath.cx/projects/overture}{http://slyi.ath.cx/projects/overture}).

% , you need a Unix or Linux machine since the
% graphics interface requires Motif (or OpenMotif) and X Windows. The array class A++/P++ should run under Windows.

Here is where you can 
% \htmladdnormallink{register}{http://www.llnl.gov/CASC/Overture/download/overture_agree.html}
\htmladdnormallink{register}{../../download/overture_agree.html}
to obtain a copy of the software. Please register and let us know what you will be using Overture
for and what machines you intend to run on.

Here are \htmladdnormallink{installation instructions}{../install/index.html}.

{\bf You cannot build Overture directly on Windows} since the
graphics interface requires Motif (or OpenMotif) and X Windows.
Here are instructions for installing Overture on a Windows machine and Ubuntu using
VirtualBox \htmladdnormallink{Installing\_Overture\_on\_Ubuntu\_10\_04\_LTS.pdf}{\documentation/Installing\_Overture\_on\_Ubuntu\_10\_04\_LTS.pdf}.

% Here is where you can 
% \htmladdnormallink{download}{http://www.llnl.gov/casc/Overture/henshaw/overtureDownload/overtureDownload.html}
% Overture and A++/P++. Please let us know what you will be using Overture
% for and what machines you intend to run on. Send mail to {\tt henshaw@llnl.gov}.

\input mailingList.tex

% \input bugList.tex

\input announcement.tex

\end{document}
