%-----------------------------------------------------------------------
%   Overture talks and publications
%-----------------------------------------------------------------------
\documentclass{article}

% \setlength{\textwidth}{9in}      % page width

\usepackage{html}

\newcommand{\publications}{../publications}
\newcommand{\documentation}{../documentation}


\begin{document}

\begin{center}
{\Large Overture Presentations, Talks and Publications} \\
~~ \\
LLNL Overlapping Grid Project \\
\htmladdnormallink{Centre for Applied Scientific Computing}{http://www.llnl.gov/casc} \\
\htmladdnormallink{Lawrence Livermore National Laboratory}{http://www.llnl.gov}  \\
\htmladdnormallink{Overture}{http://www.llnl.gov/CASC/Overture} 
\end{center}


\input announcement.tex

% ***********************************************************************************************************************************8
\section{Presentations and Talks}

\begin{itemize}


  \item \htmladdnormallink{Deforming Composite Grids for Fluid Structure Interactions}{\documentation/cse11.pdf}, 
          presented at the SIAM Conference on Computational Science and Engineering, Reno, Nevada, February 2010.

  \item \htmladdnormallink{Solving PDEs on Overlapping Grids with Overture}{\documentation/uiuc10.pdf}, 
          presented at the University of Illinois, Urbana-Champaign, September 2010.


  \item \htmladdnormallink{Recent Developments in Overture}
       {\documentation/ov08.pdf}, presented at the 9th Overset Grid Symposium, Penn State University, Pennsylvania, August 2008.

  \item \htmladdnormallink{Parallel Computation of Three-Dimensional Flows using Overlapping Grids with Adaptive Mesh Refinement}
       {\documentation/ppsc.pdf}, presented at the SIAM Conference on Parallel Processing for Scientfic Computing, Atlanta, GA, March 2008.

%  \item \htmladdnormallink{An Overture Overview}{\documentation/nasa07.pdf}, presented at NASA Ames, June 2007.

%  \item \htmladdnormallink{Overture: A Framework for Solving Partial Differential Equations on Overlapping Grids} 
%  {\documentation/ncar/ncar.htm}, presented at NCAR, August 2000.
\end{itemize}

Short courses and demos.
\begin{itemize}
  \item \htmladdnormallink{Short Course: Solving PDE's on Overlapping Grids with the Overture Framework}{\publications/OvertureShortCourse.pdf}
    (updated May 2011).

  \item \htmladdnormallink{Overture Demo Introduction}{\publications/OvertureDemoIntro.pdf}.

  \item \htmladdnormallink{Hands-on Demo of Overture and the CG Solvers}{\publications/OvertureDemo.pdf}.


\end{itemize}


% ***********************************************************************************************************************************8
\section{Publications}

Here are talks and publications in reverse chronological order. For reports serving as documentation see
the \htmladdnormallink{documentation}{http://www.llnl.gov/CASC/Overture/henshaw/overtureDocumentation/overtureDocumentation.html} page.

\begin{itemize}


% --------------- 2011


 \item {\bf Numerical Methods for Solid Mechanics on Overlapping Grids: Linear Elasticity},
         Daniel Appel\"o, Jeffrey W. Banks, William. D. Henshaw, and Donald W. Schwendeman, LLNL-JRNL-422223,  submitted for publication, 2011.
        \htmladdnormallink{AppeloBanksHenshawSchwendemanSmog2011.pdf}{\publications/AppeloBanksHenshawSchwendemanSmog2011.pdf}.


 \item {\bf A Comparative Study of Two Macro-Scale Models of Condensed-Phase Explosives}
        D. W. Schwendeman, A. K. Kapila and W. D. Henshaw, LLNL-JRNL-462102, submitted for publication,
        \htmladdnormallink{SchwendemanKapilaHenshawMacroModels2011.pdf}{\publications/SchwendemanKapilaHenshawMacroModels2011.pdf}.


 % NOTE: see papers/banks for these papers
 \item {\bf A normal mode stability analysis of numerical interface conditions for fluid/structure interaction}, 
          J. W. Banks and B. Sj{\"o}green, Commun. Comput. Phys., Volume 10, Number 2, April 2011,  
          Pages 279--304, \htmladdnormallink{BanksSjogreenFSI2011.pdf}{\publications/BanksSjogreenFSI2011.pdf}. 

 \item {\bf Two-dimensional Vlasov simulation of electron plasma wave trapping, wavefront bowing, self-focusing, and sideloss},  
            J. W. Banks, R. L. Berger, S. Brunner, B. I. Cohen and J. A. F. Hittinger, 
           Phys. Plasmas, Volume 18, Number 5, May 2011, Pages 052102, 
           \htmladdnormallink{BanksBergerBrunnerCohenHittingerVlasov2011.pdf}{\publications/BanksBergerBrunnerCohenHittingerVlasov2011.pdf}. 

 \item {\bf A Note on Compressive Limiting for Two-Material Flows}, J. W. Banks, Int. J. Numer. Meth. Fl., Volume 65, Issue 5, 2011,  
         Pages 475--608, \htmladdnormallink{BanksLimiting2011.pdf}{\publications/BanksLimiting2011.pdf}.


% --------------- 2010


 \item {\bf Parallel Performance of ADPDIS3D - A High Order Multiblock Overlapping Grid Solver for Hypersonic Turbulence},
        B. Sj\"ogreen, H.C. Yee, J. Djomehri, A. Lazanoff and W.D. Henshaw,
        Parallel Computational Fluid Dynamics, Recent Advances and Future Directions, R. Biswas editor,
        pp. 550--560, DEStech Publications, Inc, 2010.

 \item {\bf A New Class of Non-Linear, Finite-Volume Methods for Vlasov Simulation}, 
        J. W. Banks and J. A. F. Hittinger, IEEE T. Plasma  
        Sci., Volume 38, Issue 9, September 2010, Pages 2198--2207,
         \htmladdnormallink{BanksHittingerVlasov2010.pdf}{\publications/BanksHittingerVlasov2010.pdf}.

 \item {\bf On Exact Conservation for the Euler Equations with Complex Equations of State}, J. W. Banks, Commun. Comput. Phys.,  
          Volume 8, Number 5, November 2010, Pages 995--1015,
          \htmladdnormallink{BanksConservation2010.pdf}{\publications/BanksConservation2010.pdf}.


 \item {\bf A study of detonation diffraction and failure for a model of compressible two-phase reactive flow},
        D. W. Schwendeman, A. K. Kapila and W. D. Henshaw,
        Combustion Theory and Modeling, {\bf 14}, pp. 331--366, 2010, 
        \htmladdnormallink{SchwendemanKapilaHenshawMPRXN2010.pdf}{\publications/SchwendemanKapilaHenshawMPRXN2010.pdf}.

  \item {\bf Tear film dynamics on an eye-shaped domain II: Flux boundary conditions}, 
         K.L. Maki, R.L. Braun, P.~Ucciferro, W.D. Henshaw, P.E. King-Smith, 
         Journal of Fluid Mechanics, 647:361--390, 2010.

  \item {\bf Tear film dynamics on an eye-shaped domain I: Pressure boundary conditions},
      K.L. Maki, R.L. Braun, W.D. Henshaw, P.E. King-Smith, Mathematical Medicine and Biology, 2010.

% --------------- 2009

 \item {\bf A Composite Grid Solver for Conjugate Heat Transfer in Fluid-Structure Systems},
         William. D. Henshaw and Kyle K. Chand, LLNL-JRNL-407079,  Journal of Computational Physics, {\bf 228}, 2009.
        \htmladdnormallink{henshawChandCHT2009.pdf}{\publications/henshawChandCHT2009.pdf}.


 \item {\bf Computational Modeling of Blood Flow in the Trapease Inferior Vena Cava Filter},
        M.A. Singer, W.D. Henshaw and S.L. Wang, Journal of Vascular and Interventional Radiology, {\bf 20} S136--S137, 2009.

 \item {\bf Solving Partial Differential Equations on Overlapping Grids}, William D. Henshaw,
       submitted to Proceedings of Numerical Modeling of Space Plasma Flows, ASTRONUM-2008, LLNL-PROC-407183,  2008. 
        \htmladdnormallink{astronum08.pdf}{\publications/astronum08.pdf}.

 \item {\bf An Evaluation of the FCT Method for High-Speed Flows on Structured Overlapping Grids},
        Jeffrey W. Banks, William D. Henshaw and John N. Shadid, Journal of Computational Physics, {\bf 228}, 2009.
        \htmladdnormallink{OversetFCT.pdf}{\publications/OversetFCT.pdf}.

 \item {\bf Parallel Computation of Three-Dimensional Flows using Overlapping Grids with Adaptive Mesh Refinement},
         William. D. Henshaw and Donald W. Schwendeman, UCRL-JRNL-236681,
        Journal of Computational Physics, {\bf 227}, pp. 7469-7502, 2008, 
        \htmladdnormallink{henshawSchwendemanPOG2008.pdf}{\publications/henshawSchwendemanPOG2008.pdf}.

% ------------------------ 2008
 \item {\bf On Sub-linear Convergence for Linearly Degenerate Waves in Capturing Schemes}, J. W. Banks, T. Aslam and W. J. Rider, J.  
         Comput. Phys., Volume 227, Issue 14, July 2008, Pages 6985--7002,
      \htmladdnormallink{BanksAslamRiderSubLinear2008.pdf}{\publications/BanksAslamRiderSubLinear2008.pdf}.


 \item {\bf On Cylindrically Converging Shock Waves Shaped by Obstacles},
         Veronica Eliasson, William D. Henshaw and Daniel Appel\"o,
        Physica D: Nonlinear Phenomena, {\bf 237}, pp. 2203--2209, 2008, 
        \htmladdnormallink{EliassonHenshawAppelo2008.pdf}{\publications/EliassonHenshawAppelo2008.pdf}.

 \item {\bf A Study of Detonation Propagation and Diffraction with Compliant Confinement},
         Jeffrey W. Banks, William. D. Henshaw, Donald W. Schwendeman, and Ashwana K. Kapila,
        Combustion Theory and Modeling, {\bf 12}, pp. 769-808, 2008, 
        \htmladdnormallink{mfRXN.pdf}{\publications/mfRXN.pdf}.

 \item {\bf A Study of Detonation Diffraction in the Ignition-and-Growth Model},
         A.K. Kapila, D.W. Schwendeman, J.B. Bdzil and W.D. Henshaw,
        Combustion Theory and Modeling, {\bf 11}, pp. 781-822, 2007, 
        \htmladdnormallink{diffraction5sch.pdf}{\publications/diffraction5sch.pdf}.

 \item {\bf A High-Resolution Godunov Method for Compressible Multi-Material Flow on Overlapping Grids},
         Jeffrey W. Banks, Donald W. Schwendeman, Ashwana K. Kapila  and William. D. Henshaw,
        Journal of Computational Physics, {\bf 223}, pp. 262-297, 2007, 
        \htmladdnormallink{mfJWL.pdf}{\publications/mfJWL.pdf}.

 \item {\bf Detonation Diffraction, Dead Zones and the Ignition-and-Growth Model},
        G. de Oliveira, A.K. Kapila, D.W. Schwendeman, J.B. Bdzil, W.D. Henshaw and C.M. Tarver, 
        Proc. 13th International Detonation Symposium, 2006, to appear, 
        \htmladdnormallink{DetSymp06Rev2.pdf}{\publications/DetSymp06Rev2.pdf}.

 \item {\bf A High-Order Accurate Parallel Solver for {Maxwell}'s Equations on Overlapping Grids}, 
   William. D. Henshaw,
   UCRL-JRNL-215684, SIAM Journal of Scientific Computing, {\bf 28}, pp. 1730-1765, 2006.
   \htmladdnormallink{henshawMaxwell2006.pdf}{\publications/henshawMaxwell2006.pdf}.


 \item {\bf Moving Overlapping Grids with Adaptive Mesh Refinement for High-Speed Reactive and Non-reactive Flow}, 
         William. D. Henshaw, and Donald W. Schwendeman, UCRL-JRNL-215227, 
        Journal of Computational Physics, {\bf 216}, pp. 744-779, 2006, 
        \htmladdnormallink{mog2005.pdf}{\publications/mog2005.pdf}.

 \item {\bf Overlapping Grids for Solving PDEs on Complex Moving Geometry}, William. D. Henshaw,
         talk view-graphs, UCRL-PRES-213210 (2005), \htmladdnormallink{henshawNggcfs05.pdf}{\publications/henshawNggcfs05.pdf}.

 \item {\bf Interoperability and Interchangeability in the Overture Framework}, Kyle K. Chand,
         SIAM CSE Conference, 
         talk view-graphs, UCRL-PRES-209519 (2005), \htmladdnormallink{chandCSE05.pdf}{\publications/chandCSE05.pdf}.

 \item {\bf Composite Hybrid Grids in the Overture Framework}, Kyle K. Chand, 
         $7^{th}$ Symposium on Overset Composite Grid and Solution Technology,
         talk view-graphs, UCRL-PRES-206456 (2004), \htmladdnormallink{kchand.overset04.pdf}{\publications/kchand.overset04.pdf}.

 \item {\bf Adaptive Mesh Refinement On Overlapping Grids}, William. D. Henshaw,
         talk view-graphs, UCRL-PRES-204772 (2004), \htmladdnormallink{henshawAMROG.pdf}{\publications/henshawAMROG.pdf}.

 \item {\bf On Multigrid for Overlapping Grids}, William. D. Henshaw,
   UCRL-JRNL-201940 (2004), (SIAM Journal of Scientific Computing, {\bf 26}, 2005),
   \htmladdnormallink{automg.pdf}{\publications/automg.pdf}.

  \item {\bf A second order accurate embedded boundary method for the wave equation with Dirichlet data},
   Heinz-Otto Kreiss and N. Anders Petersson,
   2004, UCRL-JRNL-202686, (submitted to SIAM J. Sci. Comput.)
   \htmladdnormallink{DirichletWave.pdf}{\publications/DirichletWave.pdf}.

  \item {\bf Solution Adaptive Mesh Optimization Using Algebraic Mesh Quality Metrics}, Kyle K. Chand,
    $4^{th}$ Symposium on Trends in Unstructured Meshing, UCRL-PRES-154602,(2003),\htmladdnormallink{K.Chand.Optimization.pdf}{\publications/K.Chand.Optimization.pdf}.

  \item {\bf Difference approximations of the Neumann problem for the second order wave equation},
   Heinz-Otto Kreiss, N. Anders Petersson and Jacob Ystr\"om,
   2003, UCRL-JC-153184, (accepted for publication in SIAM J. Numer. Anal.)
   \htmladdnormallink{NeumannWave.pdf}{\publications/NeumannWave.pdf}.

  \item{\bf An Adaptive Numerical Scheme for High-Speed Reactive Flow on Overlapping Grids},
   William. D. Henshaw and Donald W. Schwendeman, {\em Journal of Computational Physics}, {\bf 191}, pp. 420--447 (2003)
   \htmladdnormallink{reactamr.pdf}{\publications/reactamr.pdf}.

  \item {\bf Numerical experiments on the interaction between the large- and  small-scale motion of the Navier-Stokes Equations}, W.D. Henshaw and H.O. Kreiss and J. Ystr\"om, SIAM Journal on Multiscale Modeling and
Simulation, {\bf 1}, pp. 119--149, 2003.
    \htmladdnormallink{HenshawKreissYstrom.pdf}{\publications/HenshawKreissYstrom.pdf}.

  \item {\bf Rapsodi: Geometry preparation and grid generation},  N. Anders
   Petersson, UCRL-PRES-152332, 2'nd SIAM
   Conference of Computational Science and Engineering, San Diego, CA, 2003.
   \htmladdnormallink{SIAM\_CSE\_2003.pdf}{\publications/SIAM\_CSE\_2003.pdf}.

  \item {\bf A Split-Step Scheme for the Incompressible Navier-Stokes Equations}, W.D. Henshaw and N. Anders Petersson.
       In ``Numerical Solutions of Incompressible Flows'', M.M. Hafez (ed.), World Scientific
       Publishing Co. Singapore, 2003.
       \htmladdnormallink{henshawPetersson2001.pdf}{\publications/henshawPetersson2001.pdf}

  \item {\bf The Terascale Simulation Tools and Technologies Centre},
      David Brown, Lori Freitag and Jim Glimm,
     A Workshop on the ACTS Collection, Berkeley, CA, September 2002, UCRL-PRES-151475,
    \htmladdnormallink{TSTT\_ACTS\_Sept\_02.pdf}{\publications/TSTT\_ACTS\_Sept\_02.pdf}.

  \item {\bf Overture Software for Solving PDEs in Complex Geometry}, David L. Brown, 
     A Workshop on the ACTS Collection, Berkeley, CA, September 2002, UCRL-PRES-150012, 
     \htmladdnormallink{ACTS\_Sept\_02.pdf}{\publications/ACTS\_Sept\_02.pdf}. 

  \item {\bf Creating Interoperable Meshing and Discretization Technology: The Terascale Simulation Tools
          and Technologies Centre}, David Brown, Lori Freitag and Jim Glimm, presented at the 
          8th International Conference on Numerical Grid
          Generation in Computational Field Simulations, Honolulu, HI, June 2002 ,UCRL-PRES-151494,
         \htmladdnormallink{TSTT-hawaii.pdf}{\publications/TSTT-hawaii.pdf}. 

  \item {\bf Difference approximations for the second order wave equation},
   Heinz-Otto Kreiss, N. Anders Petersson and Jacob Ystr\"om,
   {\em SIAM J. Numer. Anal.} {\bf 40}, pp. 1940--1967 (2002),
   \htmladdnormallink{KPYWave2002.pdf}{\publications/KPYWave2002.pdf}.

  \item {\bf Overture: An Object-Oriented Framework for Overlapping Grid Applications},
        William D. Henshaw, UCRL-JC-147889, Paper for the 2002 AIAA conference on Applied Aerodynamics, St Louis, MO,
        \htmladdnormallink{aiaa02Henshaw.pdf}{\publications/aiaa02Henshaw.pdf}.

  \item {\bf A Software Demonstration of `rap':
   Preparing CAD Geometries for Overlapping Grid Generation},  N. Anders
   Petersson, UCRL-JC-147260, Proceedings of the 8'th International
   Conference on Numerical Grid Generation in Computational 
   Field Simulations (2002).
   \htmladdnormallink{Rap2002.pdf}{\publications/Rap2002.pdf}.

  \item {\bf Generating Composite Overlapping Grids on CAD Geometries},
   William D. Henshaw, UCRL-JC-147161, Proceedings of the Eighth International Conference on Numerical Grid
   Generation in Computational Field Simulations, June 2-6, 2002, Waikiki
   Beach Marriott Resort, Honolulu, Hawaii, (2002).
  \htmladdnormallink{nggcfs2002Henshaw.pdf}{\publications/nggcfs2002Henshaw.pdf}.

  \item {\bf Component Based Hybrid Mesh Generation}, K.K. Chand, UCRL-PRES-150594, (2002),
        \htmladdnormallink{hybrid\_mesh.pdf}{\publications/hybrid\_mesh.pdf}.

  \item {\bf Overture Tools for Geometry Management and Mesh Generation}, K.K. Chand, UCRL-PRES-150595, (2002), 
        \htmladdnormallink{using\_mappings.pdf}{\publications/using\_mappings.pdf}.


  \item {\bf Stability of Pressure Boundary Conditions for Stokes and Navier--Stokes
	Equations}, N. A. Petersson, {\em J. Comput. Phys.} {\bf 172}, pp. 40-70 (2001).
	\htmladdnormallink{PeterssonNSBC.pdf}{\publications/PeterssonNSBC.pdf}.

  \item {\bf Accurate Projection Methods for the Incompressible Navier-Stokes Equations},
        D.L. Brown, R. Cortez and M.L. Minion,
        {\em Journal of Computational Physics}, {\bf 168}, pp. 464--499 (2001)
        \htmladdnormallink{BCMIIJCP.pdf}{\publications/BCMIIJCP.pdf}.

  \item {\bf Detecting Errors in CAD Surfaces and Preparing Geometries for Mesh
	Generation}, N. Anders Petersson and Kyle K. Chand, UCRL-JC-144019, Proceedings of the
	10'th International Meshing Roundtable, pp.~363-371, (2001). 
	\htmladdnormallink{PeterssonChandIMR10.pdf}{\publications/PeterssonChandIMR10.pdf}

  \item {\bf An Algorithm for Projecting Points onto a Patched CAD Model}, W.D. Henshaw, UCRL-JC-144016,
      Proceedings of the 10th International Meshing Roundtable, Newport Beach, CA, 2001.
      \htmladdnormallink{henshawIMR10.pdf}{\publications/henshawIMR10.pdf}

  \item {\bf Accuracy of Projection Methods for the Incompressible Navier-Stokes Equations}, D.L. Brown,
       2001, UCRL-JC-144037. Presented at the Half-Moon Bay conference on Incompressible flows 
       and submitted for publication. 
       \htmladdnormallink{UCRL-JC-144037DBrown.pdf}{\publications/UCRL-JC-144037DBrown.pdf}

  \item {\bf Optimizing Chimera Grids Using Genetic Algorithms}, L. Carlsson and
	N. A. Petersson, 2001, UCRL-JC-143856. (Submitted to Int. J. Numer. Meth. Eng.).
       \htmladdnormallink{PeterssonGridOpt.pdf}{\publications/PeterssonGridOpt.pdf}

  \item {\bf Hole-cutting for Three-Dimensional Overlapping Grids}, N. A. Petersson, SIAM
	J. Sci Comput. {\bf 21}, pp. 646--665 (1999). 	
       \htmladdnormallink{PeterssonHoleCutting.pdf}{\publications/PeterssonHoleCutting.pdf}

  \item {\bf An Algorithm for Assembling Overlapping Grid Systems}, N. A. Petersson, SIAM
	J. Sci. Comput. {\bf 20}, pp. 1995--2022 (1999). 
       \htmladdnormallink{PeterssonAlgorithm.pdf}{\publications/PeterssonAlgorithm.pdf}

  \item {\bf Overture: Object-Oriented Tools for Overset Grid Applications}
     D. L. Brown, William D. Henshaw and Daniel J. Quinlan,
     AIAA conference on Applied Aerodynamics,
     UCRL-JC-134018, 1999.
      \htmladdnormallink{aiaa99.ps.gz}{\publications/aiaa99.ps.gz}

   \item  G.L. Browning, W.D. Henshaw and H.-O. Kreiss, 
        {\bf A Numerical Investigation of the Interaction between the Large and Small Scales of 
        the Two-Dimensional Incompressible Navier-Stokes Equations}, LA-UR-98-1712, 1998, 
       \htmladdnormallink{perturb.ps.gz (14M)}{\publications/perturb.ps.gz}

  \item {\bf Overture: An Object-Oriented Framework for Solving Partial Differential 
                Equations on Overlapping Grids},
   D. L. Brown, William D. Henshaw and Daniel J. Quinlan,
   SIAM conference on Object Oriented Methods for Scientfic Computing,
   UCRL-JC-132017, 1999.
    \htmladdnormallink{watson98.ps.gz}{\publications/watson98.ps.gz}

   \item {\bf Overture: Object-oriented tools for solving {CFD} and combustion problems},
          D.L. Brown and William D. Henshaw,
         {\em High performance computing 1998, {G}rand challenges in computer simulation},
          Society for Computer Simulation International,A. Tentner editor, (1998)
         \htmladdnormallink{HPC98.pdf}{\publications/HPC98.pdf}.

  \item {\bf Performance of Under-resolved Two-Dimensional Incompressible Flow Simulations, II},
        M.L. Minion and D.L. Brown,
        {\em Journal of Computational Physics}, {\bf 138}, pp. 734--765 (1997)
        \htmladdnormallink{underIIJCP.pdf}{\publications/underIIJCP.pdf}.

   \item {\bf Overture: An Object Oriented Framework for Solving Partial Differential Equations},
      D. L. Brown and William D. Henshaw and Daniel J. Quinlan, presented at the 1997 ISCOPE conference
      and appeared in 
      {\em Scientific Computing in Object-Oriented Parallel Environments},
      Springer Lecture Notes in Computer Science, {\bf 1343}, 1997.

  \item {\bf OVERTURE: An Object-Oriented Software System for Solving Partial 
       Differential Equations in Serial and Parallel Environments}, 
        David L. Brown, Geoffrey S. Chesshire, William D. Henshaw and Daniel J. Quinlan, 
        Eight SIAM Conference on Parallel Processing for Scientific Computing,
       Minneapolis, Minnesota, March 14-17, 1997.
      \htmladdnormallink{SPP97.pdf} {\publications/SPP97.pdf}.

  \item {\bf Overture: An Object-Oriented System for Solving PDEs 
       in Moving Geometries on Overlapping Grids Using C++}, William D. Henshaw,  
      This article appeared in the proceedings of the First AFOSR Conference on Dynamic Motion CFD, 
     L. Sakell and D.D. Knight editors, pp. 281-290, June 1996. 
     \htmladdnormallink{dynamicMotion96Talk.ps.gz}{\publications/dynamicMotion96Talk.ps.gz}.

  \item {\bf Automatic Grid Generation}, W.D. Henshaw, {\em Acta Numerica}, {\bf 5}, pp. 121--148, 1996.
        A review article of approaches for automatic grid generation.
       \htmladdnormallink{autoGrid.pdf}{\publications/autoGrid.pdf}

  \item {\bf Stability of Some Difference Methods for the Incompressible Navier-Stokes Equations },
       UCLA Math Colloquium, February 1996.
        \htmladdnormallink{ucla96Talk.ps.gz}{\publications/ucla96Talk.ps.gz}

  \item {\bf Overture: An Object-Oriented System for Solving PDEs
        in Moving Geometries on Overlapping Grids}, William D. Henshaw, 
        presented at the Sixth International Conference
        on Numerical Combustion, New Orleans, March 1996.
        \htmladdnormallink{combustion96Talk.ps.gz}
        {\publications/combustion96Talk.ps.gz}

  \item {\bf Estimates of the Local Minimum Scale for the Incompressible {N}avier-{S}tokes Equations},
         W.D. Henshaw and H.-O. Kreiss and L.G. Reyna,
        {\em Numerical Functional Analysis and Optimization}, {\bf 16(3\&4) }, pp. 315--344 (1995).

  \item {\bf Analysis of a Difference Approximation for the Incompressible
            Navier-Stokes Equations}, W.D. Henshaw and H.-O. Kreiss, Los Alamos National Laboratory,
            LA-UR-95-3536 (1995), \htmladdnormallink{insdiv.pdf}{\publications/insdiv.pdf}.

  \item{\bf A Fourth-Order Accurate Method for the Incompressible
            {N}avier-{S}tokes Equations on Overlapping Grids}, W.D. Henshaw, 
            {\em Journal of Computational Physics}, {\bf 113}, number 1, pp. 13--25 (1994),
            \htmladdnormallink{cgicns.pdf}{\publications/cgicns.pdf}.

  \item{\bf A Fourth-Order Accurate Difference Approximation for
       the Incompressible {N}avier-{S}tokes Equations}, W.D. Henshaw and H.-O. Kreiss and L.G.M. Reyna,
       {\em Computer and Fluids}, {\bf 23} number 4, pp. 575-593 (1994),
           \htmladdnormallink{bcns.pdf}{\publications/bcns.pdf}.

  \item {\bf A Scheme for Conservative Interpolation on Overlapping Grids},
     G. Chesshire and W.D. Henshaw, {\em SIAM J. of Scientific Computing}, {\bf 15}, number 4, pp. 819--845
       (1994).

  \item {\bf An Unsplit Godunov Method for Systems of Conservation Laws on Curvilinear Overlapping
         Grids}, D.L. Brown, Losa Alamos report LA-UR-932868, (1993)  
         \htmladdnormallink{godunov.pdf}{\publications/godunov.pdf}. 

  \item {\bf Summing Logarithmic Expansions for Strong Localized Perturbations
            of Linear and Nonlinear Eigenvalue Problems},  M. J. Ward and W.D. Henshaw and J. B. Keller,
         {\em {SIAM} J. of Applied Math}, {\bf 53}, number 3, pp. 799-828 (1993).

  \item {\bf Adaptively--refined Overlapping Grids for the
                   Numerical Solution of Systems of Hyperbolic Conservation Laws}
         by Kristi D. Brislawn, David Brown, Geoffrey S. Chesshire and Jeffrey S. Saltzman. Presented
         at ICASE/LaRC workshop on Adaptive grid methods,
    \htmladdnormallink{cgamr.ps.gz}{\publications/cgamr.ps.gz}. This is from our Fortran days.

  \item {\bf On Constructing Three Dimensional Overlapping Grids with {CMPGRD}}, 
          W.D. Henshaw and G. Chesshire and M.E. Henderson,
         {\em Software Systems for Surface Modeling and Grid Generation},
       NASA Conference Publication 3143, R.E. Smith Editor, pp. 415--434 (1992).

  \item  {\bf A Numerical Study of the Propagation of Perturbations in the Solutions of the 
        2D Incompressible {N}avier-{S}tokes Equations},
         W.D. Henshaw and H.-O. Kreiss,
         {\em Third International Conference on Hyperbolic Problems},
             B. Engquist and B. Gustafsson editors, Chartwell-Bratt, pp. 54--61 (1991).


  \item {\bf Composite Overlapping Meshes for the Solution of Partial Differential Equations},
      G. Chesshire and W.D. Henshaw, {\em Journal of Computational Physics}, {\bf 90}, number 1, pp. 1--64 (1990).

  \item {\bf Smallest scale estimates for the incompressible {Navier-Stokes} equations},
   W.D. Henshaw and H.-O. Kreiss and L.G. Reyna,
   {\em Arch. Rational Mech. Anal.}, {\bf 112}, pp. 21--44, (1990).

  \item {\bf On Composite Overlapping Grids}, D.L. Brown and G. Chesshire and W.D. Henshaw and H.-O. Kreiss,
    {\em Finite Element Analysis in Fluids}, T.J. Chung and G.R. Karr Editors, UAH Press, pp. 544--559 (1989).

  \item {\bf On the smallest scale for the incompressible {Navier-Stokes} equations},
         W.D. Henshaw and H.-O. Kreiss and L.G. Reyna,
         {\em Theoretical and Computational Fluid Dynamics}, {\bf 1}, pp. 1--32 (1989).


  \item{\bf Multigrid on Composite Meshes}, W.D. Henshaw and G. Chesshire,
          {\em SIAM J. of Scientific and Statistical Computing}, {\bf 8}, number 6, pp. 914-923, (1987).

  \item {\bf Part {II}: Composite Overlapping Grid Techniques}, W.D. Henshaw,
        Ph.D. Thesis, Dept. of Applied Mathematics, California Institute of Technology (1985).

\end{itemize}




% Combustion related publications
% \begin{itemize}
%   \item 
%    L. H. Howell, R. B. Pember, P. Colella, J. P. Jessee, and W. A.
%    Fiveland, {\bf A Conservative
%    Adaptive-Mesh Algorithm for Unsteady, Combined-Mode Heat Transfer},
%    accepted for
%    publication in Num. Heat Trans., Pt. B (1999). Also available as
%    Lawrence Livermore
%    National Laboratory technical report UCRL-JC-132144. 
%     \htmladdnormallink{amrdo.pdf}{\publications/amrdo.pdf}
%   \item R. B. Pember, L. H. Howell, J. B. Bell, P. Colella, W.Y. Crutchfield, W.
%    A. Fiveland, and J. P.
%    Jessee, {\bf An Adaptive Projection Method for Unsteady, Low-Mach Number
%    Combustion},
%    accepted for publication in Comb. Sci. Tech (1999). Also available as
%    Lawrence Livermore
%    National Laboratory technical report UCRL-JC-132064.
%     \htmladdnormallink{amrcomb.pdf}{\publications/amrcomb.pdf}
% \item R. B. Pember, A. S. Almgren, J. B. Bell, P. Colella, L.H. Howell, M.
%     Lai, {\bf A Higher-Order
%     Projection Method for the Simulation of Unsteady Turbulent Nonpremixed
%     Combustion in an
%     Industrial Burner}, in Transport Phenomena in Combustion, Taylor and
%     Francis, 1996, pp.
%     1200-1211. Also available as Lawrence Livermore National Laboratory
%     technical report
%     UCRL-JC-118634. 
%     \htmladdnormallink{istp8.ps.gz}{\publications/istp8.ps.gz}
% \item R. B. Pember, A. S. Almgren, W. Y. Crutchfield, L. H. Howell, J. B.
%   Bell, P. Colella and V. E.
%   Beckner, {\bf An Embedded Boundary Method for the Modeling of Unsteady
%   Combustion in an
%   Industrial Gas-Fired Furnace}, in Proc. 1995 Fall Meeting of the Western
%   States Section of
%   the Combustion Institute, Stanford, CA, October 30-31, 1995. Also
%   available as Lawrence
%   Livermore National Laboratory technical report UCRL-JC-122177. 
%     \htmladdnormallink{embedded.pdf}{\publications/embedded.pdf}
% 
% 
% \end{itemize}



\end{document}



