\subsection{constructor}
 
\newlength{\BoxMappingIncludeArgIndent}
\begin{flushleft} \textbf{%
\settowidth{\BoxMappingIncludeArgIndent}{BoxMapping(}% 
BoxMapping( \\ 
\hspace{\BoxMappingIncludeArgIndent}const real xMin, const real xMax, \\ 
\hspace{\BoxMappingIncludeArgIndent}const real yMin, const real yMax,\\ 
\hspace{\BoxMappingIncludeArgIndent}const real zMin, const real zMax ) 
}\end{flushleft}
\begin{description}
\item[{\bf Description:}] 
    Build a rectangular box in 3D. The box can also be rotated
  around one the coordinate directions.
\item[{\bf xMin,xMax :}]  minimum and maximum values for x(xAxis)
\item[{\bf yMin,yMax :}]  minimum and maximum values for y(yAxis)
\item[{\bf zMin,zMax :}]  minimum and maximum values for z(zAxis)
\end{description}
\subsection{rotate}
 
\begin{flushleft} \textbf{%
int  \\ 
\settowidth{\BoxMappingIncludeArgIndent}{rotate(}%
rotate(const real angle, \\ 
\hspace{\BoxMappingIncludeArgIndent}const int axisOfRotation  = 2,\\ 
\hspace{\BoxMappingIncludeArgIndent}const real x0  = 0.,\\ 
\hspace{\BoxMappingIncludeArgIndent}const real y0  = 0.,\\ 
\hspace{\BoxMappingIncludeArgIndent}const real z0  = 0.)
}\end{flushleft}
\begin{description}
\item[{\bf Description:}] 
    Rotate the box around a coordinate direction.
\item[{\bf angle (input) :}]  angle in degrees.
\item[{\bf xisOfRotation (input) :}]  0,1 or 2.
\item[{\bf x0,y0,z0 (input) :}]  rotate about this point.
\end{description}
\subsection{getVertices}
 
\begin{flushleft} \textbf{%
int   \\ 
\settowidth{\BoxMappingIncludeArgIndent}{getVertices(}%
getVertices(real \& xMin, real \& xMax, real \& yMin, real \& yMax, real \& zMin, real \& zMax ) const
}\end{flushleft}
\begin{description}
\item[{\bf Purpose:}]  Return the bounds on the box.
\item[{\bf xMin, xMax, yMin, yMax, zMin, zMax (output) :}]  bounds on the box.
\end{description}
\subsection{setVertices}
 
\begin{flushleft} \textbf{%
int  \\ 
\settowidth{\BoxMappingIncludeArgIndent}{setVertices(}%
setVertices(const real \& xMin  =0.,\\ 
\hspace{\BoxMappingIncludeArgIndent}const real \& xMax  =1., \\ 
\hspace{\BoxMappingIncludeArgIndent}const real \& yMin  =0., \\ 
\hspace{\BoxMappingIncludeArgIndent}const real \& yMax  =1.,\\ 
\hspace{\BoxMappingIncludeArgIndent}const real \& zMin  =0.,\\ 
\hspace{\BoxMappingIncludeArgIndent}const real \& zMax  =1.)
}\end{flushleft}
\begin{description}
\item[{\bf Purpose:}]  Set the bounds on the box.
\item[{\bf xMin, xMax, yMin, yMax, zMin, zMax (input) :}]  bounds on the box.
\end{description}
