\subsection{Constructor}
 
\newlength{\CrossSectionMappingIncludeArgIndent}
\begin{flushleft} \textbf{%
\settowidth{\CrossSectionMappingIncludeArgIndent}{CrossSectionMapping(}% 
CrossSectionMapping(\\ 
\hspace{\CrossSectionMappingIncludeArgIndent}const real startS\_,\\ 
\hspace{\CrossSectionMappingIncludeArgIndent}const real endS\_,\\ 
\hspace{\CrossSectionMappingIncludeArgIndent}const real startAngle\_,\\ 
\hspace{\CrossSectionMappingIncludeArgIndent}const real endAngle\_,\\ 
\hspace{\CrossSectionMappingIncludeArgIndent}const real innerRadius\_ ,\\ 
\hspace{\CrossSectionMappingIncludeArgIndent}const real outerRadius\_,\\ 
\hspace{\CrossSectionMappingIncludeArgIndent}const real x0\_ ,\\ 
\hspace{\CrossSectionMappingIncludeArgIndent}const real y0\_ ,\\ 
\hspace{\CrossSectionMappingIncludeArgIndent}const real z0\_ ,\\ 
\hspace{\CrossSectionMappingIncludeArgIndent}const real length\_,\\ 
\hspace{\CrossSectionMappingIncludeArgIndent}const int domainDimension\_)
}\end{flushleft}
\begin{description}
\item[{\bf Description:}]  Default Constructor, define a mapping from cross-sections.

 Build a mapping defined by cross sections. In the {\tt general} case the cross-sections
  are defined by other Mapping's. One can also build an ellipsoid when the cross-section
 type is {\tt ellipse} or a Joukowsky wing.
 enum CrossSectionType:
 \begin{itemize}
  \item general
  \item ellipse
  \item joukowsky
 \end{itemize}

  enum Parameterization:
 \begin{description}
  \item[arcLength] : parameterize by the arc length distance between the centroids of the cross sectional curves.
  \item[index] : parameterize by the index of the cross section.
  \item[userDefined] : supply a parameterization.
 \end{description}
\end{description}
\subsection{setCrossSectionType}
 
\begin{flushleft} \textbf{%
int  \\ 
\settowidth{\CrossSectionMappingIncludeArgIndent}{setCrossSectionType(}%
setCrossSectionType(CrossSectionTypes type)
}\end{flushleft}
\begin{description}
\item[{\bf Description:}] 
   Define the cross-section type.  *this is not finished yet*
\item[{\bf type (input):}] 

\end{description}
\subsection{Constructor}
 
\begin{flushleft} \textbf{%
int  \\ 
\settowidth{\CrossSectionMappingIncludeArgIndent}{initialize(}%
initialize()
}\end{flushleft}
\begin{description}
\item[{\bf Description:}]  private routine. Initialize the parameterization for the
  cross sections.

\end{description}
